---
title: "Lab 05 Replication Notebook"
author: "Christopher Prener, Ph.D."
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
---

## Introduction
This is the replication notebook for Lab-05 from the course SOC 4650/5650: Introduction to GISc. 

## Load Dependencies
The following code loads the package dependencies for our analysis:

```{r package-load}
# tidyverse
library(ggplot2) # data plotting

# other packages
library(ggthemes) # map theme
library(here) # working directory tools
library(sf) # spatial data tools
library(viridis) # color palettes
```

## Load Data
The following code loads the data package and assigns our data to a data frame in our global environment:

```{r data-load}
housing <- st_read(here("data","STL_HOUSING_MedianAge", "Shapefile", "STL_HOUSING_MedianAge.shp"), 
                      stringsAsFactors = FALSE)
```

## Create Median Home Age Map in `R`
### Question 6
The code block below maps the data and adds a labeled legend, an appropriate theme, a title, and other map layout labels:

```{r build-map}
ggplot() +
  geom_sf(data = housing, mapping = aes(fill = ESTIMATE), color = NA) +
  scale_fill_viridis(name = "Median Age", option = "inferno") +
  theme_map(base_size = 14) +
  theme(legend.position = "right") +
  labs(
    title = "Median Age of Homes in \nSt. Louis, MO",    
    subtitle = "Christopher Prener, Ph.D.",
    caption = "Data via the U.S. Census Bureau"
  )
```

The map shows that the median age of homes in most neighborhoods is around 1940, with some post-war development in the southwest and far northern reaches of the city. The near north side and midtown area have far more recent residential development.

### Question 7
The following code exports our map to the `results/` folder:

```{r export-map}
ggsave(here("results", "medianAge.png"), dpi = 300)
```

